Visualizing the Geography of Genetic Variants

### 2016-07-01 paper.tex
updated

\caption[Schematic diagram of the Geography of Genetic Variants (GGV) browser]{Schematic diagram of the Geography of Genetic Variants (GGV) browser. We compute minor allele frequencies from publicly available population genetic datasets from the 1000 Genomes Project, Human Genome Diversity Project (HGDP) and Population Reference Sample (POPRES). These allele frequencies are stored in a SQL database along side with geographic coordinates associated with each population. The front-end visualization was created using d3 and accesses allele frequency and population meta-data from a REST API implemented in the python library flask.}\label{fig:figure1}
\end{figure}
\end{CodeChunk}

>>>>

\caption[Schematic diagram of the Geography of Genetic Variants (GGV) browser]{Schematic diagram of the Geography of Genetic Variants (GGV) browser. We compute minor allele frequencies from publicly available population genetic datasets from the 1000 Genomes Project, Human Genome Diversity Project (HGDP) and Population Reference Sample (POPRES). These allele frequencies are stored in a SQL database along side with geographic coordinates associated with each population. The front-end visualization was created using D3.js and accesses allele frequency and population meta-data from a REST API implemented in the python library flask.}\label{fig:figure1}
\end{figure}
\end{CodeChunk}
